### 2012-03-01 2.2.2.tex
More arranging.

% 2.2.2: Computational models

@@

\citet{McGowan2011} claims that the type frequency of individual syllable contact clusters in English is predicted by the change of sonority in the clusters.\footnote{I am grateful to Maria Gouskova for bringing this study to my attention.} Using a sonority scale proposed by \citet{Jespersen1904}, \citeauthor{McGowan2011} reports that clusters like [m.p], with sharply falling sonority, are more frequent than those like [t.j], with rising sonority. \citeauthor{McGowan2011} reports, however, that this accounts for only a tiny amount of the variance in frequency ($R^2 = 0.077$). Change in sonority provides no improvement to the null baseline, and so this model is not reported here.

>>>>

\subsection{Computational models}

@@

\footnote{\citet{McGowan2011} claims that the type frequency of individual syllable contact clusters in English is predicted by the change of sonority in the clusters. Using a sonority scale proposed by \citet{Jespersen1904}, \citeauthor{McGowan2011} reports that clusters like [m.p], with sharply falling sonority, are slightly more frequent than those like [t.j], with rising sonority. However, sonority of clusters accounts for only a tiny amount of the variance in frequency ($R^2 = 0.077$). Sonority distance provides no improvements to the null baseline in this task, and is not reported further. I am grateful to Maria Gouskova for bringing \citeauthor{McGowan2011}'s study to my attention.}

### 2012-03-01 3.1.2.tex
More arranging.

% 3.1.2: Labial attraction

@@

\noindent
\citeauthor{Clements1982} are suggesting that \textsc{Labial Attraction} implies that \emph{aTu}, where \emph{T} represents a non-labial consonant, should be infrequent, but this fact is not inconsistent with the formulation of the constraint by \citet{Lees1966a,Lees1996b} and \citet{Zimmer1969}; \emph{aTu} clusters do not meet \textsc{Labial Attraction}'s structural description.

>>>>

\subsection{Labial attraction}

@@

\noindent
\citeauthor{Clements1982} are suggesting that \textsc{Labial Attraction} implies that \emph{aTu}, where \emph{T} represents a non-labial consonant, should be infrequent, but this fact is not inconsistent with the formulation of the constraint by \citet{Lees1966a,Lees1966b} and \citet{Zimmer1969}; \emph{aTu} clusters do not meet \textsc{Labial Attraction}'s structural description.

### 2012-03-01 3.3.1.tex
Drastic restructuring and some writing on chapters 2-3.
More arranging.

% 3.3.1: Naturalness

@@

This has an ad hoc nature to it; 
There are two senses in which this objection is ad hoc. 
First, \citeauthor{Becker2011} appeal to no particular theory of the naturalness of processes or static constraints which excludes \textsc{Labial Attraction}. 
Secondly, this appears to be a minority view: \textsc{Labial Attraction} was considered a true generalization by early specialists
\citep[e.g.,][]{Lees1966a}, and despite \citeauthor{Zimmer1969}'s suggestive psycholinguistic results, reviewed above, it also been treated as a plausible constraint by later theorists \citep[e.g.,][]{NiChiosain1993,Ito1993,Ito1995a,Zuraw2000}.
Further, there is a real danger that if the label ``unnatural'' Labial Attraction} describes an impossible structural change or structural description, that one will fail to account for earlier forms of Turkish or sound changes therein.

>>>>

% 3.3.1: Naturalness
\subsection{Naturalness}

@@

This has an ad hoc nature to it; 
There are two senses in which this objection is ad hoc. 
First, \citeauthor{Becker2011} appeal to no particular theory of the naturalness of processes or static constraints which excludes \textsc{Labial Attraction}. 
Secondly, this appears to be a minority view: \textsc{Labial Attraction} was considered a true generalization by early specialists
\citep[e.g.,][]{Lees1966a}, and despite \citeauthor{Zimmer1969}'s suggestive psycholinguistic results, reviewed above, it also been treated as a plausible constraint by later theorists \citep[e.g.,][]{NiChiosain1993,Ito1993,Ito1995a,Zuraw2000}.
Further, there is a real danger that if the label ``unnatural'' 
%Labial Attraction} 
describes an impossible structural change or structural description, that one will fail to account for earlier forms of Turkish or sound changes therein.

%Classical Arabic adjectives often have stative verbs in which the root is imposed onto the template CaCuCa:

%\ex Arabic verbs of coming into being: \\
%\begin{tabular}{r l l l}
%a. & kabura & `become big'       & (cf. \emph{kabiːr} `big') \\
%b. & saʁiir & `become small'     & (cf. \emph{saʁiːr} `small') \\
%c. & ħasuna & `become beautiful' & (cf. \emph{ħasan} `handsome') \\
%\end{tabular}
%\xe

### 2012-03-01 4.tex
Drastic restructuring and some writing on chapters 2-3.
More arranging.

% 4: Gradient and categorical aspects of wordlikeness judgements

@@

\begin{quotation}
``...the greatest defect of classical philosophy of the mind...seems to me to be its unquestioned assumption that the properties and content of the mind are accessible to introspection.'' \citep[][22]{Chomsky1968}
\end{quotation}

>>>>

\chapter{Gradient and categorical aspects of wordlikeness judgements}
\label{gradience}

@@

%\begin{quotation}
%``...the greatest defect of classical philosophy of the mind...seems to me to be its unquestioned assumption that the properties and content of the mind are accessible to introspection.'' \citep[][22]{Chomsky1968}
%\end{quotation}

\input{4.1}
\input{4.2}
\input{4.3}
